% vim:ts=4:sw=4
% Copyright (c) 2014 Casper Ti. Vector
% Public domain.

\begin{cabstract}
	% 中文测试文字。
	% \pkuthssffaq
	人际关系总是人们生活中非常重要的一环，⼈们扩展自己的交际圈的需求⽆所不在，在如今的互联网的时代下，移动应用成为了人们进行社交活动的重要方式。为了尽可能减少用户去扩展社交圈的障碍,令⽤户可以更加有效地获取新的人际关系,很多的移动互联⽹应用尝试用不同的方式去 降低用户获取好友的难度。然⽽,这些现有的应用对于用户的信息利用不完全,往往不能提供令用户满意的效果。

	本⽂提出了⼀种通过人脸识别的技术为主，用户的的其他信息为辅助的方法来帮助用户去减少他们去扩展社交圈的难度,在本系统中,将用户的人脸看做了一个非常重要的特征，来配合其他特征来进行匹配算法，为用户推荐好友。 

针对以上的想法,本⽂实现了一种适合多移动平台，覆盖广泛的应用，并设计了不同的匹配算法,通过实验衡量其性能和用户体验。最终确定了一个比较优秀的设计 成为了一个移动互联⽹应⽤,经实验证明该应用具有良好的体验,可以面向商⽤进⼀步推⼴。
而更进一步的，由于图片流应用的火热和现在computer version技术的发展，可以根据人们在日常生活中所表现出的倾向进行学习和进一步的匹配，前景十分远大。


\end{cabstract}

\begin{eabstract}
	Personal relationship is always most important part in human's live, thus people are inclined to expand their relatioship. In the internet age, mobile application become the most popular access to communicate with others. To facilitate people developing relationship, there are a myriad ways supporing by current application to find friends. 
	However, lack of taking advantage of full of user information, the ways to find friends could not lead to a good result.

	Therefore, regarding this problem, we introduce face recognition to facilitate user extending their social circle. Recommend friends to user mainly by the features of user's face, associating with other user information. Further we devise several matching friend algorthm, implement a application suited multiple mobile platform to realize it. And the user study shows that the social application based on face recogition has a good performance to extend user social circle. 

	Moreover, this matching algorithm could achieve more higher by the development of computer version technologies.   
\end{eabstract}

